Flowchart of Current Algorithm

### 2008-10-27 docs/flowchart/flowchart.tex
now reflects that psi is computed within advect_base_pres

\item {\bf Advect Base Pressure}$[p_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [p_0^\outp]$\\
is the process by which we update the base state pressure through $\dt$ in time.
\begin{description}

\item[plane-parallel:] We discretize the base state pressure
  evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp 
\enskip,
\end{equation}
\MarginPar{shouldn't the edge states for $p_0$ have a $\inp$ or $\outp$ superscript?}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in the forcing for
the interface state calculation, but is used in the update.

@@

\item (spherical only) {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph,\star}, \psi^{\nmh}]$ 
$\rightarrow [p_0^{n+1,\star}]$.  Note that $\psi$ is not used in the spherical case.

\item Define an edge-centered $\etarho^{\nph,\star}$, cell-centered 
$(\nabla\cdot\etarho\er)^{\nph,\star}$, and cell-centered $\psi_j^{\nph,\star}$:

@@

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ \left(\uadvone \cdotb \er + w_0^{\nph,\star}\right) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}
\begin{equation}
 \psi_j^{\nph,\star} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{equation}

@@

\item (plane-parallel only only) {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph,\star},$ 
$\psi^{\nph,\star}] \rightarrow [p_0^{n+1,\star}]$.

@@

\item (spherical only) {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph}, \psi^{\nph,\star}]$ 
$\rightarrow [p_0^{n+1}]$.  Note that $\psi$ is not used in the spherical case.

\item Define an edge-centered $\etarho^{\nph}$, cell-centered 
$(\nabla\cdot\etarho\er)^{\nph}$, and a cell-centered $\psi_j^{\nph}$,

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\left(\uadvtwo \cdotb \er + w_0^{\nph}\right) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}
\begin{equation}
 \psi_j^{\nph} = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{equation}

@@

\item  (plane-parallel only) {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph}, \psi^{\nph}]$ 
$\rightarrow [p_0^{n+1}]$.

>>>>

\item {\bf Advect Base Pressure}$[p_0^\inp,w_0^\inp,\etarho^\inp] \rightarrow$ 
$[p_0^\outp,\psi^\outp]$\\
is the process by which we update the base state pressure through $\dt$ in time and
compute $\psi$.
\begin{description}

\item[plane-parallel:] First we compute a cell-centered $\psi^\outp$ using
\begin{equation}
 \psi_j^\outp = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^\inp + \eta_{\rho,j+\myhalf}^\inp\right) g \enskip .
\end{equation}
Then, we discretize the base state pressure evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\outp 
\enskip,
\end{equation}
\MarginPar{shouldn't the edge states for $p_0$ have a $\inp$ or $\outp$ superscript?}
where the interface states are again found via the procedure described
in paper II, Appendix A.

@@

\item Define an edge-centered $\etarho^{\nph,\star}$ and  cell-centered 
$(\nabla\cdot\etarho\er)^{\nph,\star}$:

@@

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ \left(\uadvone \cdotb \er + w_0^{\nph,\star}\right) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}

@@

\item {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph,\star}, \etarho^{n+\myhalf,\star}]$ 
$\rightarrow [p_0^{n+1,\star}, \psi^{\nph,\star}]$.

@@

\item Define an edge-centered $\etarho^{\nph}$ and cell-centered 
$(\nabla\cdot\etarho\er)^{\nph}$:

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\left(\uadvtwo \cdotb \er + w_0^{\nph}\right) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}

@@

\item {\bf Advect Base Pressure}$[p_0^{n}, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1}, \psi^{n+\myhalf}]$.
